\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-04-06 Drafts and notes/Attempts/Old_draft_06.tex
Major change

%============%============%============%============%
%\setlength{\columnseprule}{0.4pt}
%\setlength{\topmargin}{0cm}
%\setlength{\oddsidemargin}{.25cm}
%\setlength{\evensidemargin}{.25cm}
%\setlength{\textheight}{22.5cm}
%\setlength{\textwidth}{15.5cm}
\renewcommand{\baselinestretch}{1.05}
%============%============%============%============%
\usepackage[toc,page]{appendix}
%============%============%============%============%
\usepackage{xcolor}
\usepackage{placeins}
\usepackage{amsfonts,amsmath,amsthm}
\usepackage{amssymb,epsfig}
\usepackage{enumerate} 
\usepackage[notcite,notref]{showkeys}
\usepackage{fullpage}
%============%============%============%============%
\usepackage[utf8]{inputenc}
%\usepackage{mathpazo}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\subsection{Motivation} Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$. Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to 
\begin{equation}\label{eq:PDEeps}
    \begin{cases}
    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the (expectation) value function associated with a minimization of a stochastic optimal control problem with state-constraint. We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0$. Heuristically, the state-constraint second-order problem converges to the state-constraint first-order, which is associated with deterministic optimal control, which is described in the framework of viscosity solution as follows:
\begin{equation}\label{eq:PDE0}
    \begin{cases}
     \lambda u(x) + H(x,Du(x)) \leq 0\;\qquad\text{in}\;\Omega,\\
     \lambda u(x) + H(x,Du(x)) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
    \end{cases} \tag{PDE$_0$}
\end{equation}
Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all viscosity subsolution $v\in\rmC(\overline{\Omega})$. The problem is interesting since in the limit we no longer have blowing up behavior. In this paper, we are interested in the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0$. A boundary layer is expected to describe the behavior of convergence near the boundary.
\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary in $\mathbb{R}^n$ and $H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian. 
\begin{itemize}
    \item[$\mathrm{(A1)}$] $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
\end{itemize}
We list the assumptions on a general Hamiltonian as follow.
\begin{itemize}
    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
    \begin{equation*}
        \begin{cases}
        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
    \end{equation*}
    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
\end{itemize}

\section{Preliminaries}\label{sec:prelim} 
\subsection{Setting and simplifications} Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial$ is of class $C^2$. For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) > \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$. 
\begin{figure}[ht]
    \centering
    %\incfig{Domains}
    \def\svgwidth{0.47\columnwidth}
    \import{./figs/}{Domains.pdf_tex}
    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
    \label{fig:Domains}
\end{figure}
We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region. We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
    \end{cases}
\end{equation*}
We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.

Let $\delta_0>0$ be a fixed number such that $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is of class $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$, i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) \leq \delta_0$. We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
    \end{cases}
\end{equation*}
Let us denote
\begin{equation*}
    K := \max_{x\in \overline{\Omega}} |\Delta d(x)|.
\end{equation*}
\noindent Let us denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the operator
\begin{equation*}
    \mathcal{L}^\varepsilon[u](x) := \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x), \qquad x\in \Omega.
\end{equation*}
\subsection{Gradient estimate}

\subsection{Well-posedness of large solution for subquaratic case}

In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}. 
We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$ only, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.

@@

\noindent To find a candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the \emph{ansatz}
\begin{equation}\label{eq:ansatz}
    u(x) = C_\varepsilon d(x)^{-\alpha}, \qquad x\in \Omega
\end{equation}
as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$. Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that 
\begin{align*}
    \lambda u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
    \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|\nabla d(x)|^p,\\
    %\frac{\partial^2 u}{\partial x_i^2}(x) &\approx \alpha(\alpha+1)C_0 d(x)^{-(\alpha+2)}\left|\frac{\partial d}{\partial x_i}(x)\right|^2 -\alpha C_0 d(x)^{-(\alpha+1)}\frac{\partial ^2 d}{\partial x_i^2}(x),\\
    \varepsilon\Delta u(x) &\approx \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|\nabla d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
\end{align*}
As $|\nabla d(x)| = 1$ for $x$ near $\partial\Omega$, we see that as $x\to \partial \Omega$, the highest explosive order terms are
\begin{equation*}
        -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)} + C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}.
\end{equation*}
Setting them to zero, we deduce that
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
\end{equation*}
We can obtain the following families of supersolution on $\Omega_\delta$ and subsolution on $\Omega^\delta$ as follow. Let us denote
\begin{equation*}
    G = \left[\left(K\delta_0+(\alpha+1)\right)^\frac{1}{p-1} - (\alpha+1)^{\frac{1}{p-1}}\right]\alpha.
\end{equation*}

\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\color{red}\eta\geq G\varepsilon^{\frac{1}{p-1}}$,\color{black} we have
\begin{equation*}
    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon+\eta}{(d(x)-\delta)^\alpha} +\frac{M}{\lambda},\qquad x\in \Omega_\delta
\end{equation*}
is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$ where
\begin{equation*}
    M = \max_{\overline{\Omega}} f(x) + 2^{\alpha+1}K\alpha\varepsilon\delta_0^{-(\alpha+1)}.
\end{equation*}
\end{lem}
\begin{proof} We compute
\begin{align*}
    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M_\eta + \frac{(C_\varepsilon+\eta)^p \alpha^p}{(d(x)-\delta)^{p(\alpha+1)}}|\nabla d(x)|^p - f(x) \\
    &\qquad\qquad\qquad\qquad\quad\;\,  - \frac{\varepsilon(C_\varepsilon+\eta)\alpha(\alpha+1)}{(d(x)-\delta)^{\alpha+2}}|\nabla d(x)|^2 + \frac{\varepsilon(C_\varepsilon+\eta)\alpha}{(d(x)-\delta)^{\alpha+1}}\Delta d(x).
\end{align*}
\textcolor{red}{to be filled in...}
\end{proof}

\begin{lem}\label{lem:supersln} For each $\eta>0$ there exists $M_\eta > 0$ such that 
\begin{equation*}
    \overline{w}_{\eta,\delta}(x) \textcolor{orange}{(\underline{w}_{\eta, \delta})} = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\eta}{\lambda}, \qquad x\in \Omega^\delta 
\end{equation*}
is a supersolution $\textcolor{orange}{(subsolution)}$ of \eqref{eq:PDEeps} in $\Omega^\delta$.
\end{lem}

We divide the rest of the proof into 3 steps. We first construct a minimal solution, then a maximal solution to \eqref{eq:PDEeps}, and finally show that they are equal to conclude the existence and uniqueness of solution to \eqref{eq:PDEeps}.

>>>>

%============%============%============%============%
%\setlength{\columnseprule}{0.4pt}
%\setlength{\topmargin}{0cm}
%\setlength{\oddsidemargin}{.25cm}
%\setlength{\evensidemargin}{.25cm}
%\setlength{\textheight}{22.5cm}
%\setlength{\textwidth}{15.5cm}
\renewcommand{\baselinestretch}{1.05}
%============%============%============%============%
\usepackage[toc,page]{appendix}
%============%============%============%============%
%\usepackage{romannum}
\usepackage{xcolor}
\usepackage{placeins}
\usepackage{amsfonts,amsmath,amsthm}
\usepackage{amssymb,epsfig}
\usepackage{enumerate} 
\usepackage[notcite,notref]{showkeys}
\usepackage{fullpage}
%============%============%============%============%
\usepackage[utf8]{inputenc}
%\usepackage{mathpazo}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\subsection{Motivation} Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$. Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to 
\begin{equation}\label{eq:PDEeps}
    \begin{cases}
    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the (expectation) value function associated with a minimization of a stochastic optimal control problem with state-constraint. We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0$. Heuristically, the state-constraint second-order problem converges to the state-constraint first-order, which is associated with deterministic optimal control, which is described in the framework of viscosity solution as follows:
\begin{equation}\label{eq:PDE0}
    \begin{cases}
     \lambda u(x) + H(x,Du(x)) \leq 0\;\qquad\text{in}\;\Omega,\\
     \lambda u(x) + H(x,Du(x)) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
    \end{cases} \tag{PDE$_0$}
\end{equation}
Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all viscosity subsolution $v\in\rmC(\overline{\Omega})$. The problem is interesting since in the limit we no longer have blowing up behavior. In this paper, we are interested in the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0$. A boundary layer is expected to describe the behavior of this convergence near the boundary.
\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary in $\mathbb{R}^n$ and $H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian. 
\begin{itemize}
    \item[$\mathrm{(A1)}$] $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
\end{itemize}
We list the assumptions on a general Hamiltonian as follow.
\begin{itemize}
    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
    \begin{equation*}
        \begin{cases}
        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
    \end{equation*}
    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
\end{itemize}

\section{Preliminaries}\label{sec:prelim} 
\subsection{Setting and simplifications} Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial\Omega$ is of class $C^2$. For small $\delta>0$, we denote $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) > \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$. 
\begin{figure}[ht]
    \centering
    %\incfig{Domains}
    \def\svgwidth{0.47\columnwidth}
    \import{./figs/}{Domains.pdf_tex}
    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
    \label{fig:Domains}
\end{figure}

\noindent Let $\delta_0>0$ be a fixed number such that $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is of class $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$ (see \cite{gilbarg_elliptic_2001}), i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) \leq \delta_0$. We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that 
\begin{equation}\label{e:distance_def}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
    \end{cases}
\end{equation}
We recall that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Since $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is a viscosity solution to $|Du(x)|=1$ in $\Omega$. %we can assume that the extension $d(x)$ as also satisfies $|Dd(x)|\leq 1$ in $\Omega$. 
Let 
\begin{equation*}
    K_1 := \max_{x\in \overline{\Omega}} |\Delta d(x)| \qquad\text{and}\qquad K_2 := \max_{x\in \overline{\Omega}} |D d(x)|.
\end{equation*}
\noindent We denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the elliptic operator
\begin{equation*}
    \mathcal{L}^\varepsilon[u](x) := \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x), \qquad x\in \Omega.
\end{equation*}

\subsection{Local gradient estimate} 
We recall the local gradient bound following \cite[Appendix]{Lasry1989}. The technique being used is the classical Bernstein's method. Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $\lambda \in [0,1)$. We consider the Hamiltonian $H(x,\rho) = |\rho|^p - f(x)$ where $1<p < \infty$.

\begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u\in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$. Assume that $\lambda u(x)-f(x)\geq -K_0$ in $\Omega$, then for $\delta>0$ there exists $C_\delta = C(K_0,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that 
\begin{equation*}
    \sup_{x\in \overline{\Omega}_\delta} \Big(|u(x)|+|Du(x)|\Big) \leq C_\delta.
\end{equation*}
\end{thm}

\begin{proof} Let $\theta\in (0,1)$ be chosen later, $\varphi\in \mathrm{C}_c^\infty(\Omega)$, $0\leq \varphi\leq 1$, $\mathrm{supp}\;\varphi\subset \Omega$ and $\varphi = 1$ on $\Omega_\delta$ such that
\begin{equation}\label{e:ass_power}
    |\Delta \varphi(x)| \leq C|\varphi(x)|^\theta \qquad\text{and}\qquad |D \varphi(x)|^2 \leq C\varphi^{1+\theta}
\end{equation}
for $x\in \Omega$ and $C = C(\delta,\theta)$.
Let $w(x) = |Du(x)|^2$ for $x\in \Omega$, the goal is to derive an equation for $\varphi w$. The equation for $w$ is given by
\begin{equation*}
    -\varepsilon \Delta w + p|D u|^{p-2}D u \cdot D w + 2\lambda w - D f\cdot D u + \varepsilon |D^2u|^2 = 0 \qquad\text{in}\;\Omega.
\end{equation*}
Using that, we can derive an equation for $(\varphi w)$ as follows.
\begin{align*}
    &-\varepsilon \Delta (\varphi w) + p|D u|^{p-2}D u \cdot D (\varphi w) + 2\lambda (\varphi w) + \varepsilon \varphi|D^2u|^2 + 2\varepsilon \frac{D \varphi}{\varphi}\cdot D (\varphi w) \\
    &\qquad\qquad\qquad\qquad = \varphi(D f\cdot D u) + p|D u|^{p-2}(D u\cdot D \varphi)w -\varepsilon w \Delta \varphi + 2\varepsilon \frac{|D \varphi|^2}{\varphi}w
    \qquad\text{in}\;\mathrm{supp}\;\varphi.
\end{align*}
Assume that $\varphi w$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$ then we can assume that $x_0\in \mathrm{supp}\;\varphi$, since otherwise the maximum of $\varphi w$ over $\overline{\Omega}$ is zero. By the classical maximum principle 
\begin{equation*}
    -\varepsilon \Delta(\varphi w)(x_0)\geq 0 \qquad\text{and}\qquad |D(\varphi w)(x_0)| = 0.
\end{equation*}
Using that in the equation of $\varphi w$ above, we obtain that
\begin{equation*}
    \varepsilon \varphi|D^2u|^2 \leq  \varphi (Df\cdot Du)+ p|Du|^{p-1} |D\varphi|w + \varepsilon w |\Delta\varphi|  + 2\varepsilon  w\frac{|D\varphi|^2}{\varphi},
\end{equation*}
where all terms are evaluated at $x_0$. Using \eqref{e:ass_power} we have
\begin{equation}\label{e:est_for_D^2u}
    \varepsilon \varphi|D^2u|^2 \leq  \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + C\varepsilon w \varphi^{\theta} + 2C\varepsilon  w\varphi^\theta.
\end{equation}
By Cauchy-Schwartz inquality, we have $n|D^2u|^2\geq (\Delta u)^2$, thus if $n\varepsilon < 1$ then
\begin{equation}\label{e:est_for_D^2u_2}
    \varepsilon |D^2u|^2 \geq \frac{(\varepsilon \Delta u)^2}{n\varepsilon} \geq (\varepsilon \Delta u)^2 = \left(\lambda u + |Du|^p - f\right)^2 \geq |Du|^{2p} - 2C_0|Du|^p \geq \frac{|Du|^{2p}}{2} - 2K_0.
\end{equation}
Using \eqref{e:est_for_D^2u_2} in \eqref{e:est_for_D^2u} we obtain that
\begin{equation*}
    \varphi\left(\frac{1}{2}w^p - 2K_0\right) \leq \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + 3C\varepsilon w \varphi^{\theta}.
\end{equation*}
Multiply both sides by $\varphi^{p-1}$ we deduce that
\begin{align*}
    (\varphi w)^p \leq 4K_0\varphi^{p-1} + 2\Vert Df\Vert_{L^\infty}\varphi^p w^{\frac{1}{2}} + 2Cp \varphi^{\frac{2p+\theta - 1}{2}}w^{\frac{p+1}{2}} + 6C\varepsilon \varphi^{p+\theta - 1}w.
\end{align*}
Choose $2p+\theta -1 \geq p+1$, i.e., $p+\theta\geq 2$. This is always possible with the requirement $\theta \in (0,1)$, as $1<p <\infty$. We deduce that 
\begin{equation}\label{e:est_for_D^2u_3}
    (\varphi w)^p \leq C\left(1+ (\varphi w)^\frac{1}{2} + (\varphi w)^\frac{p+1}{2} +(\varphi w)\right)
\end{equation}
As a polynomial in $z = (\varphi w)(x_0)$, this implies that $(\varphi w)(x_0)\leq C$ where $C$ depends on coefficients of the right hand side of \eqref{e:est_for_D^2u_3}, which implies our desired gradient bound since $\overline{\Omega}_\delta\subset \mathrm{supp}\;\varphi$.
\end{proof}

\subsection{Well-posedness of large solution for subquaratic case} In this section, with the specific form of the Hamiltonian $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$, we show the existence and uniqueness of solutions to \eqref{eq:PDEeps}. 
We note that the assumption of $f$ can be relaxed to $f\in L^\infty(\Omega)$, but for the clarity of the proof we will assume $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.

@@

\noindent To find a candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the \emph{ansatz}
\begin{equation}\label{eq:ansatz}
    u(x) = C_\varepsilon d(x)^{-\alpha}, \qquad x\in \Omega
\end{equation}
as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$. Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that 
\begin{align*}
    \lambda u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
    \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|D d(x)|^p,\\
    %\frac{\partial^2 u}{\partial x_i^2}(x) &\approx \alpha(\alpha+1)C_0 d(x)^{-(\alpha+2)}\left|\frac{\partial d}{\partial x_i}(x)\right|^2 -\alpha C_0 d(x)^{-(\alpha+1)}\frac{\partial ^2 d}{\partial x_i^2}(x),\\
    \varepsilon\Delta u(x) &\approx \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|D d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
\end{align*}
As $|D d(x)| = 1$ for $x$ near $\partial\Omega$, we see that as $x\to \partial \Omega$, the highest explosive order terms are
\begin{equation*}
        -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)} + C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}.
\end{equation*}
Setting them to zero, we deduce that
\begin{equation}\label{e:relation}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}} = \frac{1}{\alpha}(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+1}.
\end{equation}
We note that $\alpha+1 = \frac{1}{p-1}$ for convenience later. Recall that $_1 = \max_{\overline{\Omega}}|\Delta d(x)|$, let us denote
\begin{equation*}
    G = \left[\left(K_1\delta_0+(\alpha+1)\right)^{\alpha+1} - (\alpha+1)^{\alpha+1}\right]\alpha.
\end{equation*}

\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\eta\geq G\varepsilon^{\alpha+1}$, we have
    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon+\eta}{(d(x)-\delta)^\alpha} +\frac{M_\varepsilon}{\lambda},\qquad x\in \Omega_\delta, 
is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$ where
\begin{equation}\label{e:M_eps}
    M_\varepsilon = \max_{\overline{\Omega}} f + 2\left(\frac{2}{\delta_0}\right)^{\alpha+1}K_1(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+2} + \left(\frac{2(\alpha+1)\varepsilon}{\delta_0}\right)^{\alpha+2}\big(2^pK_2^p+2K_2^2\big).
\end{lem}
\noindent The reason why we state this lemma again instead of just citing \cite{Lasry1989} is because we want to show that the constant $M_\varepsilon$ here can be chosen independent of $\eta$ as long as $\eta \geq G\varepsilon^{\alpha+1}$, thus $\{M_\varepsilon\}_{\varepsilon>0}$ is bounded.
\begin{proof} Recall that $p(\alpha+1) = \alpha+2$, we compute
    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) = \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} &+ M_\varepsilon + \frac{(C_\varepsilon+\eta)^p \alpha^p}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^p - f(x) \\
    &- \frac{\varepsilon(C_\varepsilon+\eta)\alpha(\alpha+1)}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^2 + \frac{\varepsilon(C_\varepsilon+\eta)\alpha}{(d(x)-\delta)^{\alpha+1}}\Delta d(x).
Regarding the relation \eqref{e:relation}, we define
    1<\nu = \left(\frac{C_\varepsilon+\eta}{C_\varepsilon}\right) \leq 2.
There are two cases to be considered.
    \item In the region where $d(x)\geq \delta_0$ then $d(x)-\delta \geq \frac{1}{2}\delta_0$, therefore 
        \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) = \frac{\lambda(C_\varepsilon + \eta)}{(d(x)-\delta)^\alpha} + M_\varepsilon &+ \frac{\alpha^pC_\varepsilon^p}{(d(x)-\delta)^{\alpha+2}}\left(\nu^{p}|Dd(x)|^p - \nu|Dd(x)|^2\right)\\
        &+\frac{\nu\varepsilon \alpha C_\varepsilon}{(d(x)-\delta)^{\alpha+1}}\Delta d(x) - f(x).
Recall that $K_2 = \max_{x\in\overline{\Omega}}|Dd(x)|$ and $1<|\nu|\leq 2$, we have
    \frac{\alpha^pC_\varepsilon^p}{(d(x)-\delta)^{\alpha+2}}\left|\nu^{p}|Dd(x)|^p - \nu|Dd(x)|^2\right| &\leq \left(\frac{2(\alpha+1)\varepsilon}{\delta_0}\right)^{\alpha+2}\big(2^pK_2^p+2K_2^2\big).
%As $|Dd(x)|\leq 1$, $\nu^p|Dd(x)|^p - \nu|Dd(x)|^2 \geq 0$ since $1<p<2$ and $\nu>1$. Finally
